---
title: 'NCAA D3 Cross Country'
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    source_code: "https://github.com/lisafishr/NCAA-D3-Cross-Country"
    theme: bootstrap
---

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
Nats19ind <- read_csv("Nats19ind.csv")
Nats19team <- read_csv("Nats19team.csv")
regions <- read_csv("regions.csv")
```


```

About
==========================


2019 Nationals by Region
==========================
Row
-------------------------------------
    
### Individuals
    
```{r, echo = FALSE}
inputPanel(
  sliderInput("slider1", label = h3("Place"), min = 1, 
        max = 277, value = c(1, 277), sep = ""),
  textInput("text", label = h3("Search"), value = NULL , placeholder = "Eg. St. Olaf")
)

renderTable({ 
Nats19ind %>% 
  select(PL, NAME, Team, TIME, Region) %>%
  filter(NAME %in% NAME[str_detect(.$NAME, input$text)] | 
         PL %in% PL[str_detect(.$PL, input$text)] | 
         Team %in% Team[str_detect(.$Team, input$text)] | 
         Region %in% Region[str_detect(.$Region, input$text)] ) %>%
  filter(PL >= input$slider1[1], PL <= input$slider1[2])
}) 

```
   
Row
-------------------------------------
    
### Regional Distribution
  
```{r}
renderPlot({
Nats19ind %>%
  filter(!is.na(PL)) %>%
  filter(PL >= input$slider1[1], PL <= input$slider1[2]) %>%
  mutate(allAmerican = ifelse(PL <= 40, "All American", "Not All American")) %>%
  mutate(allAmerican = allAmerican %>% fct_rev()) %>%
  ggplot(mapping = aes(x = Region, fill = allAmerican)) +
  geom_bar() +
  labs(title = "2019 NCAA Participants", fill = "All Americans")
})
```
  



2018 Nationals by Region
==========================
Row
-------------------------------------
    
### Individuals
    
```{r, echo = FALSE}
inputPanel(
  sliderInput("slider1", label = h3("Place"), min = 1, 
        max = 277, value = c(1, 277), sep = ""),
  textInput("text", label = h3("Search"), value = NULL , placeholder = "Eg. St. Olaf")
)

renderTable({ 
Nats19ind %>% 
  select(PL, NAME, Team, TIME, Region) %>%
  filter(NAME %in% NAME[str_detect(.$NAME, input$text)] | 
         PL %in% PL[str_detect(.$PL, input$text)] | 
         Team %in% Team[str_detect(.$Team, input$text)] | 
         Region %in% Region[str_detect(.$Region, input$text)] ) %>%
  filter(PL >= input$slider1[1], PL <= input$slider1[2])
}) 

```
   
Row
-------------------------------------
    
### Regional Distribution
  
```{r}
renderPlot({
Nats19ind %>%
  filter(!is.na(PL)) %>%
  filter(PL >= input$slider1[1], PL <= input$slider1[2]) %>%
  mutate(allAmerican = ifelse(PL <= 40, "All American", "Not All American")) %>%
  mutate(allAmerican = allAmerican %>% fct_rev()) %>%
  ggplot(mapping = aes(x = Region, fill = allAmerican)) +
  geom_bar() +
  labs(title = "2019 NCAA Participants", fill = "All Americans")
})
```
  

2017 Nationals by Region
==========================
Row
-------------------------------------
    
### Individuals
    
```{r, echo = FALSE}
inputPanel(
  sliderInput("slider1", label = h3("Place"), min = 1, 
        max = 277, value = c(1, 277), sep = ""),
  textInput("text", label = h3("Search"), value = NULL , placeholder = "Eg. St. Olaf")
)

renderTable({ 
Nats19ind %>% 
  select(PL, NAME, Team, TIME, Region) %>%
  filter(NAME %in% NAME[str_detect(.$NAME, input$text)] | 
         PL %in% PL[str_detect(.$PL, input$text)] | 
         Team %in% Team[str_detect(.$Team, input$text)] | 
         Region %in% Region[str_detect(.$Region, input$text)] ) %>%
  filter(PL >= input$slider1[1], PL <= input$slider1[2])
}) 

```
   
Row
-------------------------------------
    
### Regional Distribution
  
```{r}
renderPlot({
Nats19ind %>%
  filter(!is.na(PL)) %>%
  filter(PL >= input$slider1[1], PL <= input$slider1[2]) %>%
  mutate(allAmerican = ifelse(PL <= 40, "All American", "Not All American")) %>%
  mutate(allAmerican = allAmerican %>% fct_rev()) %>%
  ggplot(mapping = aes(x = Region, fill = allAmerican)) +
  geom_bar() +
  labs(title = "2019 NCAA Participants", fill = "All Americans")
})
```
  

2016 Nationals by Region
==========================
Row
-------------------------------------
    
### Individuals
    
```{r, echo = FALSE}
inputPanel(
  sliderInput("slider1", label = h3("Place"), min = 1, 
        max = 277, value = c(1, 277), sep = ""),
  textInput("text", label = h3("Search"), value = NULL , placeholder = "Eg. St. Olaf")
)

renderTable({ 
Nats19ind %>% 
  select(PL, NAME, Team, TIME, Region) %>%
  filter(NAME %in% NAME[str_detect(.$NAME, input$text)] | 
         PL %in% PL[str_detect(.$PL, input$text)] | 
         Team %in% Team[str_detect(.$Team, input$text)] | 
         Region %in% Region[str_detect(.$Region, input$text)] ) %>%
  filter(PL >= input$slider1[1], PL <= input$slider1[2])
}) 

```
   
Row
-------------------------------------
    
### Regional Distribution
  
```{r}
renderPlot({
Nats19ind %>%
  filter(!is.na(PL)) %>%
  filter(PL >= input$slider1[1], PL <= input$slider1[2]) %>%
  mutate(allAmerican = ifelse(PL <= 40, "All American", "Not All American")) %>%
  mutate(allAmerican = allAmerican %>% fct_rev()) %>%
  ggplot(mapping = aes(x = Region, fill = allAmerican)) +
  geom_bar() +
  labs(title = "2019 NCAA Participants", fill = "All Americans")
})
```
  

